
\section{Projects}
\infolist{Microwave Radar-based Imaging Toolbox}{Jul. 2024 - Aug. 2024}{Declan O'Loughlin, Trinity College Dublin}{Dublin, Ireland}{
\-{Reconstruction of microwave imaging signals in medical and industrial settings in Matlab.}\\
\-{Added and cleaned up the complete sample data from the 2018 research paper.}\\
\-{Created script that can prcoess the breast microwave imaging dataset from the University of Manitoba.}\\
\-{Replaced deprecated functions with their modern alternatives.}
}

\infolist{Autonomous Drone Mapping and Pathfinding}{May. 2024 - Jul. 2024}{Harun Siljak, Trinity College Dublin}{Dublin, Ireland}{
\-{Developed a Python program for the Crazyflie drone V2.0}\\
\-{Maps out an area and dynamically pathfinds between two points defined in the area.}\\
\-{Repurposed the motion sensor of a drone to detect grayscale colors.}\\
\-{Created a simulation for the program in Matlab.}
}

\infolist{Autonomous Buggy Vehicle}{Jan 2023 - Apr. 2023}{Trinity College Dublin}{Dublin, Ireland}{
\-{Designed and programmed an Arduino-based vehicle to drive autonomously.}\\
\-{C++, Github.}\\
\-{Managed a team of four to make sure goals were reached in a timely manner.}
}

\infolist{The Energy \& Water Demand Project}{Sep. 2022 - Dec. 2022}{Trinity College Dublin}{Dublin, Ireland}{
\-{Developed a solution to deliver solar energy to the rural village Kameswaram, India.}\\
\-{Discussed executability with representatives for non-profit foundation, Friend in Need India.}\\
\-{Estimated the costs of transport and maintenance for long-term support of clean energy.}
}

\infolist{Portable Sheltered Parklet}{Sep. 2022 - Dec. 2022}{Trinity College Dublin}{Dublin, Ireland}{
\-{Developed a solution to deliver solar energy to the rural village Kameswaram, India.}\\
\-{Discussed executability with representatives for non-profit foundation, Friend in Need India.}\\
\-{Estimated the costs of transport and maintenance for long-term support of clean energy.}
}